---
title: "Dessication tests (multiple species)"
author: "Miquel De Cáceres"
date: "2023-11-05"
output: html_document
---
```{r, echo = FALSE, message = FALSE, warning=FALSE, include = FALSE}
library(ggplot2)
library(cowplot)
library(medfate)


Sys.setlocale("LC_TIME", "en_US.UTF-8")
```

```{r, echo = FALSE, include = FALSE}
SpParams <- read.table(file="../Tables/SpParams.txt", sep="\t", header = TRUE)
results_sureau <- read.table(file="../Tables/results_sureau.txt", sep="\t", header = TRUE)
results_sperry <- read.table(file="../Tables/results_sperry.txt", sep="\t", header = TRUE)
results_sperry_segmented <- read.table(file="../Tables/results_sperry_segmented.txt", sep="\t", header = TRUE)

sel1  <- results_sureau$day_failure_leaf>=50
sel2  <- results_sperry$day_failure_leaf>=50
results_sureau <- results_sureau[sel1 & sel2, ]
results_sperry <- results_sperry[sel1 & sel2, ]

results_sureau$model <- "Sureau"
results_sperry$model <- "Sperry"
results <- dplyr::bind_rows(results_sperry, results_sureau)
results <- results |>
  dplyr::rename(Name = Species) |>
  dplyr::left_join(SpParams, by= "Name")
SpParams <- SpParams[sel1 & sel2, ]
```


*Trait correlations*:

A positive relationship exists between Gs_P50 and VC_P50, as well as between VC_P50 and Gswmax. Relationships between Gs_P50 and maximum stomatal conductance (Gswmax) or whole-plant hydraulic conductance (Plant_kmax) have been enforced by construction.

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 7, warning=FALSE}
g1 <- ggplot(SpParams)+
  geom_point(aes(x = VCstem_P50, y = Gs_P50))+
  geom_abline(intercept= 0, slope = 1)+
  theme_bw()
g2 <- ggplot(SpParams)+
  geom_point(aes(x = VCstem_P50, y = Gswmax))+
  geom_abline(intercept= 0, slope = 1)+
  theme_bw()
g3 <- ggplot(SpParams)+
  geom_point(aes(x = Gs_P50, y = Gswmax))+
  geom_abline(intercept= 0, slope = 1)+
  theme_bw()
g4 <- ggplot(SpParams)+
  geom_point(aes(x = Gs_P50, y = plant_kmax))+
  theme_bw()
plot_grid(g1, g2, g3, g4, nrow = 2)
```


*Model coincidence in closure and failure*:

Sperry has a tendency to close stomata earlier, and a tendency to earlier hydraulic failure than Sureau.

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE, message = FALSE}
g2 <- ggplot()+
  geom_point(aes(x = results_sureau$day_failure_leaf, y = results_sperry$day_failure_leaf, col = SpParams$VCstem_P50 - SpParams$Gs_P50))+
  geom_smooth(aes(x = results_sureau$day_closure, y = results_sperry$day_closure), method = "lm")+
  geom_abline(intercept = 0, slope = 1)+
  scale_color_continuous("P50 diff")+
  ylim(c(0,365))+xlim(c(0,365))+
  ylab("Time to hydraulic failure in SPERRY")+
  xlab("Time to hydraulic failure in SUREAU")+
  theme_bw()
g1 <- ggplot()+
  geom_point(aes(x = results_sureau$day_closure, y = results_sperry$day_closure, col = SpParams$VCstem_P50 - SpParams$Gs_P50))+
  geom_smooth(aes(x = results_sureau$day_closure, y = results_sperry$day_closure), method = "lm")+
  scale_color_continuous("P50 diff")+
  geom_abline(intercept = 0, slope = 1)+
  ylim(c(0,365))+xlim(c(0,365))+
  ylab("Time to stomatal closure in SPERRY")+
  xlab("Time to stomatal closure in SUREAU")+
  theme_bw()
l <- get_legend(g1)
plot_grid(g1+theme(legend.position = "none"), 
          g2+theme(legend.position = "none"), 
          l, nrow = 1, rel_widths = c(1,1,0.3))
```


*Relationship between VC_P50 or Gs_P50 and Psi_min*:

The left panel shows how Sperry model decides leaf water potential trying to maintain a safety margin with respect to VC_P50, which is not the case in Sureau. The right panel illustrates that Sureau determines a leaf water potential less negative than Gs_P50, whereas Sperry leads to more negative leaf water potential than Gs_P50. In both panels, the black line indicates the 1:1 relationship.

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
g1 <- ggplot(results)+
  geom_point(aes(x = VCstem_P50, y = psi_min, col = model))+
  geom_abline(intercept = 0, slope = 1)+
  xlab("Water potential corresponding to 50% stem PLC (MPa)")+ ylab("Initial midday water potential (MPa)")+
  scale_color_discrete("")+
  theme_bw()+theme(legend.position = c(0.85,0.15))
g2 <- ggplot(results)+
  geom_point(aes(x = Gs_P50, y = psi_min, col = model))+
  geom_abline(intercept = 0, slope = 1)+
  xlab("Water potential corresponding to 50% Gs (MPa)")+ ylab("Initial midday water potential (MPa)")+
  scale_color_discrete("")+
  theme_bw()+theme(legend.position = "none")
plot_grid(g1, g2, nrow = 1)
```


*Relationship between Gs_P50 and day to closure and hydraulic failure*:

There is a negative linear relationship in both models between Gs_P50 and the time to stomatal closure. More negative Gs_P50 resulting in later closure. This may be the result of the positive relationship between Gs_P50 and Gswmax or Plant_kmax, with less negative Gs_P50 values coordinated with an increased transpiration and, hence, an earlier closure. The relationship with Gs_P50 is less strong in the case of the time to hydraulic failure.

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE, message = FALSE}
g1 <- ggplot(results)+
  geom_point(aes(x = Gs_P50, y = day_closure, col = model))+
  geom_smooth(aes(x = Gs_P50, y = day_closure, col = model))+
  xlab("Water potential corresponding to 50% Gs (MPa)")+ ylab("Time to stomatal closure")+
  ylim(c(0,365))+
  scale_color_discrete("")+
  theme_bw()+theme(legend.position = c(0.8,0.8))
g2 <- ggplot(results)+
  geom_point(aes(x = Gs_P50, y = day_failure_stem, col = model))+
  geom_smooth(aes(x = Gs_P50, y = day_failure_stem, col = model))+
  xlab("Water potential corresponding to 50% Gs (MPa)")+ ylab("Time to hydraulic failure")+
  ylim(c(0,365))+
  scale_color_discrete("")+
  theme_bw()+theme(legend.position = "none")
plot_grid(g1, g2, nrow = 1)
```


*Relationship between VC_P50 and day to closure and hydraulic failure*:

There seems to be no obvious correspondence between VC_P50 and the time to stomatal closure. In Sureau there is, however, a relationship with the time to hydraulic failure, the more resistant species indeed resisting longer. Apparently, this relationship does not occur in Sperry.

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE, message = FALSE}
g1 <- ggplot(results)+
  geom_point(aes(x = VCstem_P50, y = day_closure, col = model))+
  geom_smooth(aes(x = VCstem_P50, y = day_closure, col = model))+
  xlab("Water potential corresponding to 50% stem PLC (MPa)")+ ylab("Time to stomatal closure")+
  ylim(c(0,365))+
  scale_color_discrete("")+
  theme_bw()+theme(legend.position = c(0.8,0.8))
g2 <- ggplot(results)+
  geom_point(aes(x = VCstem_P50, y = day_failure_stem, col = model))+
  geom_smooth(aes(x = VCstem_P50, y = day_failure_stem, col = model))+
  xlab("Water potential corresponding to 50% stem PLC (MPa)")+ ylab("Time to hydraulic failure")+
  ylim(c(0,365))+
  scale_color_discrete("")+
  theme_bw()+theme(legend.position = "none")
plot_grid(g1, g2, nrow = 1)
```

*Relationship between k_plant and day to closure / hydraulic failure*:

There is a strong relationship in both models between whole-plant hydraulic conductance and the time to stomatal closure, with a higher hydraulic efficiency leading to an earlier closure. The relationship is less obvious in the case of hydraulic failure (other traits become more relevant)

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE, message = FALSE}
g1 <- ggplot(results)+
  geom_point(aes(x = actual_kplant, y = day_closure, col = model))+
  geom_smooth(aes(x = actual_kplant, y = day_closure, col = model))+
  ylab("Time to stomatal closure")+ xlab("Whole-plant hydraulic conductance")+
  scale_color_discrete("")+
  theme_bw()+theme(legend.position = c(0.8,0.8))
g2 <- ggplot(results)+
  geom_point(aes(x = actual_kplant, y = day_failure_stem, col = model))+
  geom_smooth(aes(x = actual_kplant, y = day_failure_stem, col = model))+
  ylab("Time to hydraulic failure")+ xlab("Whole-plant hydraulic conductance")+
  scale_color_discrete("")+
  theme_bw()+theme(legend.position ="none")
plot_grid(g1, g2, nrow = 1)
```

*Relationship between maximum stomatal conductance and day to closure / hydraulic failure*:

Patterns are similar than with kplant

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE, message = FALSE}
g1 <- ggplot(results)+
  geom_point(aes(x = Gswmax, y = day_closure, col = model))+
  geom_smooth(aes(x = Gswmax, y = day_closure, col = model))+
  ylab("Time to stomatal closure")+ xlab("Maximum stomatal conductance")+
  scale_color_discrete("")+
  theme_bw()+theme(legend.position = c(0.8,0.8))
g2 <- ggplot(results)+
  geom_point(aes(x = Gswmax, y = day_failure_stem, col = model))+
  geom_smooth(aes(x = Gswmax, y = day_failure_stem, col = model))+
  ylab("Time to hydraulic failure")+ xlab("Maximum stomatal conductance")+
  scale_color_discrete("")+
  theme_bw()+theme(legend.position ="none")
plot_grid(g1, g2, nrow = 1)
```



