---
title: "Dessication tests on experimental plots"
author: "Miquel De Cáceres"
date: "2023-11-03"
output: 
  html_document:
    toc: true
---
```{r, echo = FALSE, message = FALSE, warning=FALSE, include = FALSE}
library(ggplot2)
library(cowplot)
library(medfate)
Sys.setlocale("LC_TIME", "en_US.UTF-8")
```


## Puéchabon

```{r, echo = FALSE}
S1 <- readRDS("../Rdata/Puechabon/Dessication_Puechabon_Sperry.rds")
S2 <- readRDS("../Rdata/Puechabon/Dessication_Puechabon_Sureau_Baldocchi.rds")
```

*Vulnerability curves*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- hydraulics_vulnerabilityCurvePlot(S1$spwbInput, type = "stem", vulnerabilityFunction = "Weibull",speciesNames = TRUE)
p1  <- p1 + theme(legend.position = "none")+labs(title="Sperry (Weibull)")
p2 <- hydraulics_vulnerabilityCurvePlot(S2$spwbInput, type = "stem", vulnerabilityFunction = "Sigmoid",speciesNames = TRUE)+theme(legend.position = "none")+labs(title="Sureau (Sigmoid)")
plot_grid(p1, p2, nrow = 1)
```

*Soil water potentials*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "SoilPsi")+ylim(c(-10,0))+labs(title="Sperry")+theme(legend.position = c(0.8,0.7))
p2 <- plot(S2, "SoilPsi")+ylim(c(-10,0))+labs(title="Sureau")+theme(legend.position = c(0.8,0.7))
plot_grid(p1, p2, nrow = 1)
```

*Hydraulic redistribution*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "HydraulicRedistribution")+ylim(c(0,0.8))+theme(legend.position = c(0.8,0.7))+labs(title="Sperry")
p2 <- plot(S2, "HydraulicRedistribution")+ylim(c(0,0.8))+theme(legend.position = c(0.8,0.7))+labs(title="Sureau")
plot_grid(p1, p2, nrow = 1)
```

*Leaf water potential range*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "LeafPsiRange", bySpecies = TRUE)+ylim(c(-10,0))+theme(legend.position = "none")+labs(title="Sperry")
p2 <- plot(S2, "LeafPsiRange", bySpecies = TRUE)+ylim(c(-10,0))+theme(legend.position = "none")+labs(title="Sureau")
plot_grid(p1, p2, nrow = 1)
```

*Plant transpiration*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "Transpiration", bySpecies = TRUE)+ylim(c(0,3.5))+theme(legend.position = "none")+labs(title="Sperry")
p2 <- plot(S2, "Transpiration", bySpecies = TRUE)+ylim(c(0,3.5))+theme(legend.position = "none")+labs(title="Sureau")
plot_grid(p1, p2, nrow = 1)
```

*Stomatal conductance* (shade leaves forced to behave as sunlit leaves):

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "LeafStomatalConductance", bySpecies = TRUE, subdaily = TRUE)+ylim(c(0,0.3))+theme(legend.position = "none")+labs(title="Sperry")
p2 <- plot(S2, "LeafStomatalConductance", bySpecies = TRUE, subdaily = TRUE)+ylim(c(0,0.3))+theme(legend.position = "none")+labs(title="Sureau")
plot_grid(p1, p2, nrow = 1)
```


*Stem PLC*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "StemPLC", bySpecies = TRUE)+ylim(c(0,100))+theme(legend.position = "none")+labs(title="Sperry")
p2 <- plot(S2, "StemPLC", bySpecies = TRUE)+ylim(c(0,100))+theme(legend.position = "none")+labs(title="Sureau")
plot_grid(p1, p2, nrow = 1)
```

*Soil-plant conductance*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "SoilPlantConductance", bySpecies = TRUE)+ylim(c(0,0.8))+theme(legend.position = "none")+labs(title="Sperry")
p2 <- plot(S2, "SoilPlantConductance", bySpecies = TRUE)+ylim(c(0,0.8))+theme(legend.position = "none")+labs(title="Sureau")
plot_grid(p1, p2, nrow = 1)
```



## Yatir

```{r, echo = FALSE}
S1 <- readRDS("../Rdata/Yatir/Dessication_Yatir_Sperry.rds")
S2 <- readRDS("../Rdata/Yatir/Dessication_Yatir_Sureau_Baldocchi.rds")
```

*Vulnerability curves*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- hydraulics_vulnerabilityCurvePlot(S1$spwbInput, type = "stem", vulnerabilityFunction = "Weibull",speciesNames = TRUE)
p1  <- p1 + theme(legend.position = "none")+labs(title="Sperry (Weibull)")
p2 <- hydraulics_vulnerabilityCurvePlot(S2$spwbInput, type = "stem", vulnerabilityFunction = "Sigmoid",speciesNames = TRUE)+theme(legend.position = "none")+labs(title="Sureau (Sigmoid)")
plot_grid(p1, p2, nrow = 1)
```

*Soil water potentials*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "SoilPsi")+ylim(c(-10,0))+labs(title="Sperry")+theme(legend.position = c(0.8,0.7))
p2 <- plot(S2, "SoilPsi")+ylim(c(-10,0))+labs(title="Sureau")+theme(legend.position = c(0.8,0.7))
plot_grid(p1, p2, nrow = 1)
```

*Hydraulic redistribution*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "HydraulicRedistribution")+ylim(c(0,0.8))+theme(legend.position = c(0.8,0.7))+labs(title="Sperry")
p2 <- plot(S2, "HydraulicRedistribution")+ylim(c(0,0.8))+theme(legend.position = c(0.8,0.7))+labs(title="Sureau")
plot_grid(p1, p2, nrow = 1)
```

*Leaf water potential range*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "LeafPsiRange", bySpecies = TRUE)+ylim(c(-10,0))+theme(legend.position = "none")+labs(title="Sperry")
p2 <- plot(S2, "LeafPsiRange", bySpecies = TRUE)+ylim(c(-10,0))+theme(legend.position = "none")+labs(title="Sureau")
plot_grid(p1, p2, nrow = 1)
```

*Plant transpiration*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "Transpiration", bySpecies = TRUE)+ylim(c(0,3.5))+theme(legend.position = "none")+labs(title="Sperry")
p2 <- plot(S2, "Transpiration", bySpecies = TRUE)+ylim(c(0,3.5))+theme(legend.position = "none")+labs(title="Sureau")
plot_grid(p1, p2, nrow = 1)
```

*Stomatal conductance* (shade leaves forced to behave as sunlit leaves):

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "LeafStomatalConductance", bySpecies = TRUE, subdaily = TRUE)+ylim(c(0,0.3))+theme(legend.position = "none")+labs(title="Sperry")
p2 <- plot(S2, "LeafStomatalConductance", bySpecies = TRUE, subdaily = TRUE)+ylim(c(0,0.3))+theme(legend.position = "none")+labs(title="Sureau")
plot_grid(p1, p2, nrow = 1)
```


*Stem PLC*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "StemPLC", bySpecies = TRUE)+ylim(c(0,100))+theme(legend.position = "none")+labs(title="Sperry")
p2 <- plot(S2, "StemPLC", bySpecies = TRUE)+ylim(c(0,100))+theme(legend.position = "none")+labs(title="Sureau")
plot_grid(p1, p2, nrow = 1)
```

*Soil-plant conductance*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "SoilPlantConductance", bySpecies = TRUE)+ylim(c(0,0.8))+theme(legend.position = "none")+labs(title="Sperry")
p2 <- plot(S2, "SoilPlantConductance", bySpecies = TRUE)+ylim(c(0,0.8))+theme(legend.position = "none")+labs(title="Sureau")
plot_grid(p1, p2, nrow = 1)
```


## Hesse

```{r, echo = FALSE}
S1 <- readRDS("../Rdata/Hesse/Dessication_Hesse_Sperry.rds")
S2 <- readRDS("../Rdata/Hesse/Dessication_Hesse_Sureau_Baldocchi.rds")
```

*Vulnerability curves*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- hydraulics_vulnerabilityCurvePlot(S1$spwbInput, type = "stem", vulnerabilityFunction = "Weibull",speciesNames = TRUE)
p1  <- p1 + theme(legend.position = "none")+labs(title="Sperry (Weibull)")
p2 <- hydraulics_vulnerabilityCurvePlot(S2$spwbInput, type = "stem", vulnerabilityFunction = "Sigmoid",speciesNames = TRUE)+theme(legend.position = "none")+labs(title="Sureau (Sigmoid)")
plot_grid(p1, p2, nrow = 1)
```

*Soil water potentials*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "SoilPsi")+ylim(c(-5,0))+labs(title="Sperry")+theme(legend.position = "none")
p2 <- plot(S2, "SoilPsi")+ylim(c(-5,0))+labs(title="Sureau")+theme(legend.position = c(0.2,0.25))
plot_grid(p1, p2, nrow = 1)
```

*Hydraulic redistribution*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "HydraulicRedistribution")+ylim(c(0,1.3))+theme(legend.position = "none")+labs(title="Sperry")
p2 <- plot(S2, "HydraulicRedistribution")+ylim(c(0,1.3))+theme(legend.position = c(0.8,0.7))+labs(title="Sureau")
plot_grid(p1, p2, nrow = 1)
```

*Leaf water potential range*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "LeafPsiRange", bySpecies = TRUE)+ylim(c(-5,0))+theme(legend.position = "none")+labs(title="Sperry")
p2 <- plot(S2, "LeafPsiRange", bySpecies = TRUE)+ylim(c(-5,0))+theme(legend.position = "none")+labs(title="Sureau")
plot_grid(p1, p2, nrow = 1)
```

*Plant transpiration*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "Transpiration", bySpecies = TRUE)+ylim(c(0,3.5))+theme(legend.position = "none")+labs(title="Sperry")
p2 <- plot(S2, "Transpiration", bySpecies = TRUE)+ylim(c(0,3.5))+theme(legend.position = "none")+labs(title="Sureau")
plot_grid(p1, p2, nrow = 1)
```

*Stomatal conductance* (shade leaves forced to behave as sunlit leaves):

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "LeafStomatalConductance", bySpecies = TRUE, subdaily = TRUE)+ylim(c(0,0.3))+theme(legend.position = "none")+labs(title="Sperry")
p2 <- plot(S2, "LeafStomatalConductance", bySpecies = TRUE, subdaily = TRUE)+ylim(c(0,0.3))+theme(legend.position = "none")+labs(title="Sureau")
plot_grid(p1, p2, nrow = 1)
```


*Stem PLC*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "StemPLC", bySpecies = TRUE)+ylim(c(0,100))+theme(legend.position = "none")+labs(title="Sperry")
p2 <- plot(S2, "StemPLC", bySpecies = TRUE)+ylim(c(0,100))+theme(legend.position = "none")+labs(title="Sureau")
plot_grid(p1, p2, nrow = 1)
```

*Soil-plant conductance*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "SoilPlantConductance", bySpecies = TRUE)+ylim(c(0,1))+theme(legend.position = "none")+labs(title="Sperry")
p2 <- plot(S2, "SoilPlantConductance", bySpecies = TRUE)+ylim(c(0,1))+theme(legend.position = "none")+labs(title="Sureau")
plot_grid(p1, p2, nrow = 1)
```


## Font-Blanche

```{r, echo = FALSE}
S1 <- readRDS("../Rdata/FontBlanche/Dessication_FontBlanche_Sperry_onepool.rds")
# S1p <- readRDS("../Rdata/FontBlanche/Dessication_FontBlanche_Sperry_partialpools.rds")
S2 <- readRDS("../Rdata/FontBlanche/Dessication_FontBlanche_Sureau_Baldocchi_onepool.rds")
# S2p <- readRDS("../Rdata/FontBlanche/Dessication_FontBlanche_Sureau_Baldocchi_partialpools.rds")
```

*Vulnerability curves*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- hydraulics_vulnerabilityCurvePlot(S1$spwbInput, type = "stem", vulnerabilityFunction = "Weibull",speciesNames = TRUE)
l <- get_legend(p1)
p1  <- p1 + theme(legend.position = "none")+labs(title="Sperry (Weibull)")
p2 <- hydraulics_vulnerabilityCurvePlot(S2$spwbInput, type = "stem", vulnerabilityFunction = "Sigmoid",speciesNames = TRUE)+theme(legend.position = "none")+labs(title="Sureau (Sigmoid)")
plot_grid(p1, p2, l, nrow = 1, rel_widths = c(1,1,0.4))
```

*Soil water potentials*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "SoilPsi")+ylim(c(-10,0))+theme(legend.position = c(0.8,0.7))+labs(title="Sperry")
p2 <- plot(S2, "SoilPsi")+ylim(c(-10,0))+theme(legend.position = c(0.8,0.7))+labs(title="Sureau")
plot_grid(p1, p2, nrow = 1)
```


*Hydraulic redistribution*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "HydraulicRedistribution")+ylim(c(0,0.87))+theme(legend.position = c(0.8,0.7))+labs(title="Sperry")
p2 <- plot(S2, "HydraulicRedistribution")+ylim(c(0,0.87))+theme(legend.position = c(0.8,0.7))+labs(title="Sureau")
plot_grid(p1, p2, nrow = 1)
```

*Leaf water potential range*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "LeafPsiRange", bySpecies = TRUE)+ylim(c(-10,0))
l <- get_legend(p1)
p1 <- p1+theme(legend.position = "none")+labs(title="Sperry")
p2 <- plot(S2, "LeafPsiRange", bySpecies = TRUE)+ylim(c(-10,0))+theme(legend.position = "none")+labs(title="Sureau")
plot_grid(p1, p2, l, nrow = 1, rel_widths = c(1,1,0.4))
```

*Plant transpiration*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "Transpiration", bySpecies = TRUE)+ylim(c(0,5))+theme(legend.position = "none")+labs(title="Sperry")
p2 <- plot(S2, "Transpiration", bySpecies = TRUE)+ylim(c(0,5))+theme(legend.position = "none")+labs(title="Sureau")
plot_grid(p1, p2, l, nrow = 1, rel_widths = c(1,1,0.4))
```

*Stomatal conductance* (shade leaves forced to behave as sunlit leaves):

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "LeafStomatalConductance", bySpecies = TRUE, subdaily = TRUE)+ylim(c(0,0.3))+theme(legend.position = "none")+labs(title="Sperry")
p2 <- plot(S2, "LeafStomatalConductance", bySpecies = TRUE, subdaily = TRUE)+ylim(c(0,0.3))+theme(legend.position = "none")+labs(title="Sureau")
plot_grid(p1, p2, l, nrow = 1, rel_widths = c(1,1,0.4))
```


*Stem PLC*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "StemPLC", bySpecies = TRUE)+ylim(c(0,100))+theme(legend.position = "none")+labs(title="Sperry")
p2 <- plot(S2, "StemPLC", bySpecies = TRUE)+ylim(c(0,100))+theme(legend.position = "none")+labs(title="Sureau")
plot_grid(p1, p2, l, nrow = 1, rel_widths = c(1,1,0.4))
```

*Soil-plant conductance*:

```{r, echo=FALSE, fig = TRUE, fig.width=8, fig.height = 3.5, warning=FALSE}
p1 <- plot(S1, "SoilPlantConductance", bySpecies = TRUE)+ylim(c(0,1.5))+theme(legend.position = "none")+labs(title="Sperry")
p2 <- plot(S2, "SoilPlantConductance", bySpecies = TRUE)+ylim(c(0,1.5))+theme(legend.position = "none")+labs(title="Sureau")
plot_grid(p1, p2, l, nrow = 1, rel_widths = c(1,1,0.4))
```
